Software variability in fMRI analysis:\\ comparing between-tool and numerical errors

### 2021-12-03 paper/paper.tex
Update figures

Summary statistics for the group-level unthresholded and thresholded
t-statistics are reported in Table~\ref{table:pipeline-stats}. For each
tool pair (A, B), BT variability was significantly larger than machine
error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
signed-rank test p=0 for all tests, t-test p~\textless~$10^{-163}$ for all
tests).

@@

%%%%%%%%%% Var. of Unthresh %%%%%%%%
\begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \centering
      \includegraphics[width=\textwidth]{figures/std/gl-unthresh.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
    and difference between them (\textbf{C}). \tristan{Add XY plots for each map}}
    \label{fig:unthresh-maps}
    \end{minipage}}
  \end{figure*}

@@

  Summary statistics for subject-level unthresholded t-statistics maps are
  reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
  maps, BT variability was consistently larger than WT variability
  \tristan{report statistical tests}.

@@

  As for the group maps, BT and WT variability appeared moderately
  correlated for all subjects (Figure~\ref{fig:unthresh-correlation-allsbj}, 
  R in [0.442, 0.612], p=0.0 for all
  subjects).
  \tristan{Add the subject XY plots as supplementary material}

@@

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
        WT is computed at the virtual precision of t=17 bits.\tristan{merge with figure with brain maps}}
    \label{fig:gnp-mni}
    \end{minipage}}
  \end{figure}

  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \caption{
        Voxel-wise comparison of BT and WT variabilty. WT is computed with FSL at the virtual precision of t=17 bits.}
    \label{fig:unthresh-correlation-gvp}
    \end{minipage}}
  \end{figure*}

@@

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}).}
      \label{fig:thresh-maps}
      \end{minipage}}
    \end{figure*}

    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
    \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \centering
      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
      \caption{Confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation.}
      \label{fig:cm-thresh}
    \end{minipage}}
    \end{figure*}

@@

\tristan{Add SPM and AFNI replication figure here.}

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
    \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \end{subfigure}
    \caption{
      Voxel-wise comparison of BT and WT variabilty subject by subject. \tristan{update figure}}
  \label{fig:unthresh-correlation-allsbj}
  \end{minipage}}
\end{figure*}

>>>>

Summary statistics for the group-level unthresholded and thresholded
t-statistics are reported in Table~\ref{table:pipeline-stats}. For each
tool pair (A, B), BT variability was significantly larger than machine
error in tool A or B, in both thresholded and unthresholded maps (Wilcoxon
signed-rank test p~\textless~$10^{-162}$ for all tests, t-test p=0 for all
tests).

@@

%%%%%%%%%% Var. of Unthresh %%%%%%%%
\begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=\textwidth]{figures/std/gl-unthresh.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}
      \hfill
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{figures/std-corr-unthresh-plot.png}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
      \end{subfigure}

    \caption{Unthresholded group-level variability computed between tools (\textbf{A}) and within tools (\textbf{B}),
    and difference between them (\textbf{C}).}
    \label{fig:unthresh-maps}
    \end{minipage}}
  \end{figure*}

@@

  Summary statistics for subject-level unthresholded t-statistics maps are
  reported in Table~\ref{table:unthresh-maps-subjects}. As for group-level
  maps, BT variability was consistently larger than WT variability (Wilcoxon
  signed-rank test p~\textless~$10^{-160}$ for all tests, t-test p=0 for all
  tests).

@@

  As for the group maps, BT and WT variability appeared moderately
  correlated for all subjects (Figure~\ref{fig:unthresh-correlation-allsbj}, 
  R in [0.442, 0.612], p=0.0 for all
  subjects).

@@

  %%%%%%%%%% plot different precisions%%%%%%%%
  \begin{figure*}[ht]
    \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
      \begin{subfigure}[ht]{\textwidth}
        \centering
        \includegraphics[width=.75\textwidth]{figures/bg_global_precision.pdf}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        \hfill
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=.8\textwidth]{figures/std-corr-unthresh-vp17-plot.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \end{subfigure}
        %\caption{Standard deviation of thresholded t-statistics map on template surface}
        \caption{Unthresholded group t-statistics standard deviations computed between tools (\textbf{A}) and within tools (\textbf{B}), and difference between them (\textbf{C}).
        WT is computed at the virtual precision of t=17 bits.}
    \label{fig:gnp-mni}
    \end{minipage}}
  \end{figure*}

@@

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \begin{subfigure}[ht]{\textwidth}
          \centering
          \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
          %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
          \hfill
          \begin{subfigure}[ht]{\textwidth}
            \centering
            \includegraphics[width=.9\textwidth]{figures/dice_analysis-plot.png}
            %\caption{Standard deviation of thresholded t-statistics map on template surface}
          \end{subfigure}
        \centering
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}). The confusion matrices of activation instability
      in BT and WT among the 360 regions from the HCP-MMP1.0 parcellation is represented in the bottom row.}
      \label{fig:thresh-maps}
      \end{minipage}}
    \end{figure*}

@@

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
  \centering
  \includegraphics[width=\textwidth]{figures/replication-diffs.png}
  \caption{Differences between replicated and original results obtained in~\cite{bowring2019exploring} 
  of unthresholded group-level t-statistics for SPM (left) and AFNI (right).}
  \label{fig:replication-diff}
\end{minipage}}
\end{figure*}

\begin{figure*}[ht]
  \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
    \begin{subfigure}[ht]{\textwidth}
      \centering
      \includegraphics[width=.6\textwidth]{figures/sbj-std-corr-unthresh-plot.png}
      %\caption{Standard deviation of thresholded t-statistics map on template surface}
    \end{subfigure}
    \caption{Voxel-wise comparison of BT and WT variabilty for 16 subjects.}
  \label{fig:unthresh-correlation-allsbj}
  \end{minipage}}
\end{figure*}
